\documentclass{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{microtype}

\title{Senior Project: \\ Life Book}
\author{English 4}
\date{Spring 2019}

\pagenumbering{gobble}

\begin{document}

\maketitle

\setcounter{secnumdepth}{0}

\section{Overview}

  Your final project for English 4 is to capture your life
  experiences in a personal work of literature by making a book using
  both writing and images. This will be your high school ``Life
  Book.''  The point of this project is to create an artifact of value
  to you in the years ahead, something that shows your history and
  perspective as you launch yourself into an independent life. This is
  a big milestone for you: it is good to contemplate the past as your
  prepare for the future.

\section{Requirements}

  The requirements are simple. Select twenty pictures and print or
  paste them onto sheets of paper. For each picture, write a label that sums it up in a short sentence, then include a more meaningful caption
  that describes the picture and its story. Write as if your
  audience is your future self -- you upon discovering this book in a
  box in your attic fifty years in the future, when your memories of
  high school are mostly, if not almost entirely, forgotten (this will
  happen).

  I will grade this based on fulfillment of the requirements and the
  evidence of aesthetic value you place in the book. At this point in
  the course, you know what it means to make something literary:
  strive to perform this maneuver in your work.
  
\section{Work Time and Deadline}

  You will have some time to work on this in class but it is
  impossible to complete this project without doing work on your
  own. I cannot print pictures or text for you. I have limited
  materials to exercise your creativity: be resourceful.

  The deadline for this book is at the end of Senior Exams, June 3.
  This allows you to include your senior week activities if you
  like, but it also means you have to get them to me somehow after
  classes end. I recommend leaving them in my box at the front
  office. Of course, you are welcome to turn them in early.

  No matter what, if I don't have a life book from you by June 8 when
  I check my box after school, I will enter
  an ``F'' for you final exam grade in power school. This is
  non-negotiable.

\vfill

\noindent\emph{Enjoy this. It's my intention to send you off with a
  meaninful, interesting, and worthwhile project. You may not
  understand this now, but this life book will become incredibly
  meaningful as you age. The more seriously you take this assignment,
  and the more fun you have with it, the more you will thank yourself
  in the future.}

\end{document}
